Recpature distances

### 2025-08-18 recaptureanalysis/recaps.Rmd
updating recapture analyses

recaps = read_excel("data/Running Delta Smelt Catch_2023-09-05.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)

@@

recaps2 = left_join(recaps, select(release, -TotalReleased), by = "ReleaseEvent") %>%
  mutate(DaysSinceRelease = SampleDate - ReleaseDate,
         Type = case_when(ReleaseMethod == "Unknown" ~ "Unknown",
                          ReleaseMethod == "NA" ~ "Wild/unmarked",
                          TRUE ~ Type))

str(recaps)

@@

```
```{r}

@@

turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
summary(turbm)
plot(allEffects(turbm))
#Huh, so percentage recaptures is correlated to turbidity (marginal), but not release type. Distance is correlated to release type, but not turbidity.

>>>>

recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)

@@

recaps2 = left_join(recaps, select(release, -TotalReleased), by = "ReleaseEvent") %>%
  mutate(DaysSinceRelease = SampleDate - ReleaseDate,
         Type = case_when(ReleaseMethod == "Unknown" ~ "Unknown",
                          ReleaseMethod == "NA" ~ "Wild/unmarked",
                          TRUE ~ Type)) %>%
  select(-c(`...25`:`...32`))

str(recaps2)

@@

@@

turbm = lm(RecapRate ~ weekturb + Type2, data = releasestat)
summary(turbm)
plot(allEffects(turbm))
#Huh, so percentage recaptures is highly to turbidityy.

turbm2 = lmer(RecapRate ~ log(weekturb) + (1|BroodYear), data = releasestat)
summary(turbm2)
plot(allEffects(turbm2))

ggplot(releasestat, aes(x = log(weekturb), y = RecapRate))+
  geom_point(aes(shape = as.factor(BroodYear)))+ geom_smooth(method = "lm")
